### 2018-12-26 revisions/review-responses.tex

        %---------------------------------------------------------------------
        \question  Page 20, line 351: It is more than just the Pu isotopes that 
        makes the spectrum harder? What about the other MAs etc?
        \begin{solution}
        		Thank you for the excellent point. The corrected sentence reads thus:

		        The neutron energy spectrum at equilibrium is harder than at startup due
		         to plutonium and other strong absorbers accumulation in the core during 
		         reactor operation.  
        \end{solution}

        %---------------------------------------------------------------------
        \question  Fig 12: units on y-axis?
        \begin{solution}
                Thanks for catching this. Units $\frac{n}{cm^2 s}$ has been added.
        \end{solution}

        %---------------------------------------------------------------------
        \question  Page 24, line 389: Should that be ``233U'' and not ``233Th''?
        \begin{solution}
                Yes, we meant $^{233}$U production. The typo has been fixed.
        \end{solution}

        %---------------------------------------------------------------------
        \question  Table 5: Please provide some comments on the uncertainties - 
        where do they come from? Also, the ``reference'' results need to state 
        whether ``initial'' or ``equilibrium''
        \begin{solution}
                In the Table 5 added information that reference column contains data for initial 					fuel salt composition. Details about uncertainties has been added:

                Uncertainty for each temperature coefficient was obtain by propagating 			  				statistical error for effective multiplication factor calculation (confidence
                 interval $\pm$1.9 pcm) provided by SERPENT2 and also appears in Table 5.
        \end{solution}

        %---------------------------------------------------------------------
        \question  Page 26, line 425: ``Relatively large'' compared with what? 
        Perhaps results for an LWR case would be a good basis for comparison?
        \begin{solution}
                Sentence has been extended as follows:

                ... the total temperature coefficient of reactivity is relatively large and
                 negative during reactor operation (comparing with conventional PWR which 							temperature coefficient about -1.71 pcm/$^\circ$F $\approx$ -3.08 pcm/K 							\cite{forget_integral_2018}), despite positive MTC, and affords excellent 
                 reactor stability and control.
        \end{solution}

### 2018-12-26 results.tex
Reviewer #1 85% edits implemented #32

$^{233}$Th production in the core. The thorium-232 then $\beta$-decays to 

@@

Uncertainty for each temperature coefficient also appears in 

@@

\begin{tabularx}{\textwidth}{ m | s | s | x } \hline
   Reactivity coefficient [pcm/K]  & Initial      & Equilibrium  & Reference 

@@

The fuel temperature coefficient (FTC) is negative for both initial and 
equilibrium fuel compositions due to thermal Doppler broadening of the resonance 
capture cross sections in the thorium. This is in good agreement with earlier 
research \cite{robertson_conceptual_1971,park_whole_2015}. The moderator 
temperature coefficient (MTC) is positive for the startup composition and decreases 
during reactor operation because of spectrum hardening with fuel depletion. 
Finally, the total temperature coefficient of reactivity is negative for both 
cases, but decreases during reactor operation due to spectral shift. In 
summary, even after 20 years of operation the total temperature coefficient of 
reactivity is relatively large and negative during reactor operation, despite 
positive MTC, and affords excellent reactor stability and control.

>>>>

$^{233}$U production in the core. The thorium-233 produced after $^{232}$Th 
captured neutron then $\beta$-decays to 

@@

Uncertainty for each temperature coefficient was obtain by propagating statistical 
 error for effective multiplication factor calculation (confidence interval for K$_{eff}$
 is $\pm$1.9 pcm) provided by SERPENT2 and also appears in 

@@

\begin{tabularx}{\textwidth}{ s | s | s | s } \hline
   Reactivity coefficient [pcm/K]  & Initial      & Equilibrium  & Reference \qquad (initial)

@@

The fuel temperature coefficient (FTC) is negative for both initial and 
equilibrium fuel compositions due to thermal Doppler broadening of the resonance 
capture cross sections in the thorium. This is in good agreement with earlier 
research \cite{robertson_conceptual_1971,park_whole_2015}. The moderator 
temperature coefficient (MTC) is positive for the startup composition and decreases 
during reactor operation because of spectrum hardening with fuel depletion. 
Finally, the total temperature coefficient of reactivity is negative for both 
cases, but decreases during reactor operation due to spectral shift. In 
summary, even after 20 years of operation the total temperature coefficient of 
reactivity is relatively large and negative during reactor operation (comparing with conventional PWR which temperature coefficient about -1.71 pcm/$^\circ$F $\approx$ -3.08 pcm/K \cite{forget_integral_2018}), despite positive MTC, and affords excellent reactor stability and control.
